The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-05-29 manuscript/manuscript.tex
Before re-run the sample with n>4.5

\begin{document}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\efr{$R_{\mathrm{eff}}$}
\def\galfit{{\sc Galfit}}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lhost{$L_{\rm host}$}
\def\jcap{Journal of Cosmology and Astroparticle Physics}
\def\halpha{${\it H}\alpha$}
\def\hbeta{${\it H}\beta$}
\def\sersic{S\'ersic}
\def\lenstronomy{{\sc Lenstronomy}}
\def\Reff{{$R_{\mathrm{eff}}$}}
\def\kms{km~s$^{\rm -1}$}
\def\sigstar{{$\sigma_*$}}
\def\smass{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\sint}{$\sigma_{\rm int}$}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}  %For share same footnote
\makeatother

@@

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}

\begin{abstract}

The tight correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of  a sample of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. \textcolor{blue}{We enlarge the sample using previously published measurements and compare to the local to infer their evolution. We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation. We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$. Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today. This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity. The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.}

@@

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations. It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.

In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed quasars, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.

In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest~\citep{DeG++15}. In practice, we aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  In this redshift range, we measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. Given the high-quality and sample size of our data, we can test whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e. $\sim0.23$ dex,][]{Schulze2014}.

The paper is organized as follows. We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}. We describe the observation and collect the PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass and compared to the local samples. Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.

@@

\section{Sample selection and \mbh}
\label{sec:data}
%How the samples are selection.\\
%Where are they from?
%\\The redshift range? In a table?

%We aim to study the relation between the BH masses (\mbh) and their host galaxy properties including luminosities (\lhost) and stellar mass (\smass) to redshift at $z>1$. For this propose,

We focus on the broad-line (type-1) AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields. We select the broad-line AGNs at redshift region $1.2<z<1.7$ which cover a BH range $7.5<{\rm log}$\mbh $<8.5$ \textcolor{blue}{(BH mass estimated using \halpha\ emission line).} We present the selection window that used to choose the sample in Figure~\ref{fig:selection} and list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}. Overall, our final sample is composed of 32 new observations by \hst/WFC3.

\begin{figure}
\centering
{
\includegraphics[height=0.4\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
\textcolor{red}{Figure needs to be updated.} We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. For comparing propose, we plot the high$-z$ luminous SDSS QSO samples from the reference \citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

\begin{deluxetable*}{llccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of Observation} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}&
\colhead{Observing date}&
\colhead{Expousre time (s)}
\\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
Column 6: The observing start date.
}
\end{deluxetable*}

The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

The Near IR spectra of our target AGNs are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010}, covering the wavelength range 0.9-1.8~$\mu m$. The FMOS survey provides the best \mbh\ estimates by \halpha\ and \hbeta\ lines out to $z\sim1.7$~\citep{Greene2005, Matsuoka2013, Nobuta2012}. Note that \citet{Schulze2018} has investigate the \halpha\ and \hbeta\ emission-line properties using the multi-object spectrograph Subaru/FMOS. We referred to that paper for the details of continuum fitting and emission line modeling. Since the other compared AGNs in the literature used different calibrations of the virial method, we compare the difference among the recipes by \citet{Schulze2018, McG++08, Ding2017b} and adopt a list of consistent ones to cross-calibrate the \mbh\ for all the samples, in order to avoid any systematic bias in Section~\ref{mbh}.

We aim to collect the \mbh-\lhost\ and \mbh-\smass\ relations of our samples and comparing to the ones at different redshift. 
For comparison with the local relation, we use the local AGN measurements by \citet{Ben++10} and \citet{Bennert++2011} (hereafter, B10 and B11) to define our zero-point. The sample by B10 consists of 19 \mbh-\lhost\ measured with reliable \mbh\ measured using reverberation-mapped (uncertainty level $\sim0.15$ dex). The work of B11 contains 25 \mbh-\smass\ local active AGNs, where the \mbh\ are measured from the single-epoch method (\mbh\ uncertainty level $\sim0.4$ dex). To increase the local \smass\ and \mbh\ to the higher range, we also include 30 inactive galaxies (mainly ellipticals or S0) as measured by \citet{H+R04} (hereafter HR04).

It is worth noting that in the local comparison sample, the bulge mass is equivalent to the total stellar mass for the local comparison sample. In other words, our local comparison is the \mbh-\smass$_{Bulge}$ and not those involving total quantities.

We include in our analysis published samples at intermediate redshift range to understand the redshift evolution of these correlations. We select samples that were analyzed by members of our team, in order to ensure uniform measurements. The intermediate redshift AGNs that we consider include, for the \mbh-\lhost\ relation, 52 objects published by \citet{Park15} at $0.36<z<0.57$ and 27 objects published by \citet{Bennert11, SS13} at $0.5<z<1.9$. Moreover, \citet{Bennert11, SS13} also derive the \smass\ for the 27 objects which enable us to compare to the \mbh-\smass\ relation.

\subsection{BH masses}
\label{mbh}
 %Our selected systems are broad-line (type-1) AGNs whose \mbh\ can be estimated from single-epoch spectroscopy using the so-called virial method \textcolor{blue}{FMOS (e.g. McLure 2002; Shen 2013)}. This estimation is achieved by the assumption that the empirical scaling size of the BLR and the line-of-sight velocity width can be inferred in turn continuum luminosity ($L _{\lambda_{\rm line}}$) and emission line width (FWHM), respectively.
To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s. $<0.03$~dex) between the two references. Moreover, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ has better agreement. Thus, we adopt the virial formalism from \citet{Schulze2018}:

>>>>

\begin{document}
\def\lcdm{$\Lambda$CDM}
\def\hst{{\it HST}}
\def\efr{$R_{\mathrm{eff}}$}
\def\galfit{{\sc Galfit}}
\def\mbh{$\mathcal M_{\rm BH}$}
\def\lhost{$L_{\rm host}$}
\def\jcap{Journal of Cosmology and Astroparticle Physics}
\def\halpha{${\it H}\alpha$}
\def\hbeta{${\it H}\beta$}
\def\sersic{S\'ersic}
\def\lenstronomy{{\sc Lenstronomy}}
\def\Reff{{$R_{\mathrm{eff}}$}}
\def\kms{km~s$^{\rm -1}$}
\def\sigstar{{$\sigma_*$}}
\def\smass{{$M_*$}}
\newcommand{\Mgii}{Mg$_{\rm II}$}
\newcommand{\Civ}{C$_{\rm IV}$}
\newcommand{\sint}{$\sigma_{\rm int}$}
\newcommand{\angstrom}{\text{\normalfont\AA}}
\makeatletter
\newcommand\footnoteref[1]{\protected@xdef\@thefnmark{\ref{#1}}\@footnotemark}  %For share same footnote
\makeatother

@@

\author{Xuheng Ding\altaffilmark{1, 2}, John Silverman\altaffilmark{3}, Tommaso Treu\altaffilmark{1}, Andreas Schulze\altaffilmark{6}, Malte Schramm\altaffilmark{6}, Simon Birrer\altaffilmark{1}, Daeseong Park{7}, Knud Jahnke, Federica Duras\altaffilmark{4, 5}, Angela Bongiorno\altaffilmark{5}, et al.
 }
 \email{dxh@astro.ucla.edu}
\altaffiltext{1}{Department of Physics and Astronomy, University of California, Los Angeles, CA, 90095-1547, USA}
\altaffiltext{2}{School of Physics and Technology, Wuhan University, Wuhan 430072, China}
\altaffiltext{3}{Kavli Institute for the Physics and Mathematics of the Universe, The University of Tokyo, Kashiwa, Japan 277-8583 (Kavli IPMU, WPI)}
\altaffiltext{4}{Dipartimento di Matematica e Fisica, UniversitÃ Roma Tre, via della Vasca Navale 84, I-00146, Roma, Italy}
\altaffiltext{5}{INAF Osservatorio Astronomico di Roma, via Frascati 33, 00040 Monteporzio Catone, Italy}
\altaffiltext{6}{National Astronomical Observatory of Japan, Mitaka, Tokyo 181-8588, Japan}
\altaffiltext{7}{\textcolor{blue}{To be updated}}
\begin{abstract}

The correlations between the mass of a supermassive black hole (\mbh) and its host galaxy properties (e.g. stellar mass \smass, luminosity \lhost) suggests an evolutionary connection. A powerful way to test this co-evolution hypothesis is to trace the correlations back in cosmic time. For this purpose, we obtained multi-band {\it Hubble Space Telescope} of 32 X-ray-selected broad-line (type-1) AGN at $1.2<z<1.7$ (look-back time 8-10 Gyrs). By applying state-of-the-art tools to the images we obtained accurate host galaxy luminosity and stellar mass. The black hole mass (\mbh) is based on published near-infrared spectroscopic observations of the broad \halpha~and \hbeta~emission lines, which avoids potential unknown systematic uncertainties associated with the less well calibrated UV lines \Civ\ or \Mgii, commonly used at these redshifts. We enlarge the sample using previously published measurements and compare their \mbh-\smass~and \mbh-\lhost~relations to the local to infer their evolution. We find the \mbh-\smass\ relation by our distant sample is inconsistent with the local \mbh-\smass$_{\rm, bluge}$ relation. We take selection effect into account to fit this offset as \mbh/\smass$\propto(1+z)^\gamma$, and obtain $\gamma = 0.80\pm0.30$. Considering that there is evidence showing our sample are composed of bulge and disk components, our result indicates BHs 8-10 Gyrs ago reside in bulges, if not entire galaxies, which contain lower \smass\ than today. This indication also exist in the \mbh-\lhost\ relation, once account for the passive evolution of the host luminosity. The evolution of both correlations is consistent with a scenario where the black hole grows first, followed by morphological transformations of host galaxies from late to early-types.

@@

A powerful way to understand the origin of these correlations is to study them as a function of redshift, determining how and when they emerged and evolved over cosmic time~\citep[e.g.,][]{TMB04,Sal++06,Woo++06, Jah++09,SS13}. During the past decade, there has been much progress on this front at $z<1$ using type 1 AGNs. For example, the work by \citet{Park15, Tre++07, Pen++06qsob} demonstrated that \mbh\ at fixed mass resided in less luminous galaxies than today. This offset can be explained by a scenario in which supermassive BHs were built up first with galaxy then growing around their deep potential wells. Similarly, the works by \citet{Bennert11, Woo++08} supported this general scenario from the observation of the \mbh-\smass and \mbh-\sigstar relations. \textcolor{red}{[More reference to be added, such as positive evolution for Merloni et al. and other high-z studies such as Peng, non-evolution for Mechtley et al. Xuheng also need to also mention the observables some are stellar mass while others are velocity dispersion.
]}It should be kept in mind, however, that the evolution is detected at low significance given the considerable error bars, and some studies report results consistent with no evolution given their larger error bars \citet{SS13, Sun2015, Cisternas2011}.

In order to make progress, it is important to reduce as much as possible the uncertainties and take great care of selection effects and systematic errors. First, one needs to deal with the inherent uncertainties in BH mass estimates using the so-called ``virial" method. In particular, many studies rely on \mbh\ estimates using the \Civ\ (or \Mgii) line that may have unknown systematics, such as non-gravitational component of the BLR gas dynamics, when compared to local samples with masses based on broad Balmer lines~\citep[i.e. \halpha\ and \hbeta,][]{Schulze2018, Baskin2005, Trakhtenbrot2012}. Second, since the host information is swamped by the bright nuclear light, measuring the host galaxy properties is challenging. Great care is required for modeling the point spread function and whenever possible it is beneficial to study lensed AGNs, since lensing magnifies the host image to lensed arcs~\citep{Pen++06qsob, Ding2017a, Ding2017b}. Last but not least, the selection function needs to be taken into account when interpreting the observations~\citep{Treu2007, Lauer2007}. For instance, it has been demonstrated~\citep{Schulze2011, Schulze2014} that selecting bright AGNs at high redshift results in display steeper slopes than random ones, suggesting the selecting effects can exhibit faster evolution than a random sample. It is also important to consider the selection function when comparing the observed scaling relations with simulated ones~\citep{DeG++15}.
\textcolor{blue}{
In this study, we aim to make progress by making use of a large sample with high-quality data both for the measurement of both the host properties and the \mbh, extending to the highest redshifts where evolutionary effects should be strongest.}%~\citep{DeG++15}.

The paper is organized as follows. We briefly describe the sample selection and the BH mass of the sample in Section~\ref{sec:data}. We describe the observation and collect the PSF library in Section~\ref{observation}. In Section~\ref{sec:analysis} we decompose our sample and study the host galaxy surface photometry. In Section~\ref{sec:result}, we use the multi-band host magnitudes to infer their stellar population, which we applied to derive the rest-frame R band \lhost\ and \smass\ and compared to the local samples. Discussion and conclusion are presented in Section~\ref{sec:dis} and Section~\ref{sec:sum}.

@@

\section{Experimental design}
\label{sec:data}
%Our study overcomes the limitations of previous studies in the following way. First, to minimize selection bias, we select AGNs that fall below the knee of the black hole mass function. Second, we estimate \mbh\ using Balmer lines which avoids potential systematic uncertainties in the UV-based estimators. Third, our X-ray selected sample has lower nuclear-to-host ratios which facilitate the galaxy mass measurements. Moreover, 21/32 systems in our sample have two-band \hst\ data (i.e. WFC3+ACS), whose multi-band information provides reliable K-correction and stellar mass inference. 
We aim to determine whether AGNs have begun to couple to their host galaxy at $1.2<z<1.7$, an epoch when supermassive BH close to its peak accretion history~\citep{Aird2015}.  
We design to choose our sample that meets the following criterion to overcome the limitations of previous studies.
\begin{enumerate}
\item A sample of broad-line (type-1) AGNs that fall well below the knee of the black how mass function to minimize the bias which could raised by the selection effect.
\item Sufficient Eddington ratios to assure the AGN contains accreting black hole.
\item Balmer lines are available to estimate their \mbh, which avoids potential systematic uncertainties in the UV-based estimators \citep{Greene2005}.
\item X-ray selected sample results in lower nuclear-to-host ratios facilitating the galaxy mass measurements.
\item Images of the host galaxy observed by adopted \hst/WFC3 above the 4000 \angstrom\ break, given their redshift range.
\item The large proportion of the sample has multi-band \hst\ imaging, providing extra color information to achieve reliable K-correction and stellar mass inference. 
\end{enumerate}

In redshift range $1.2<z<1.7$, we will measure 32 host galaxies properties using \hst\ imaging data, and estimate their \mbh\ based on the robust \halpha\ and \hbeta, using the multi-object spectrograph Subaru/FMOS. Given the high-quality and sample size of our data, we are capable of testing whether the growth of BH predates that of the host by a factor of at least $1.7$ \citep[i.e. $\sim0.23$ dex,][]{Schulze2014}.

\subsection{Target selection}
We focus on broad-line AGNs as provided by the X-ray coverage of COSMOS~\citep{Civano2016}, (E)-CDFS-S~\citep{Lehmer2005, Xue2011}, and SXDS~\citep{Ueda2008} fields, with X-ray flux limited in 0.5-8 keV.
The Near IR spectra of the AGNs in these fields are available from the survey of Subaru's Fiber Multi-Object Spectrograph~\citep[FMOS, ][]{Kimura2010, Matsuoka2013, Nobuta2012}, covering the wavelength range 0.9-1.8~$\mu m$ which provides the favorable \halpha\ and \hbeta\ lines out to $z\sim1.7$ to estimates the \mbh. More recently, \citet{Schulze2018} present near-IR spectroscopy of a large sample of 243 X-ray AGN in these field. We referred to that paper for the details of continuum fitting and emission line modeling. 
\textcolor{red}{John comments to be included:
[These were first identified through optical spectroscopy in most cases with zCOSMOS bright of faint samples (see Merloni et al. 2007) and then followed up with NIR spectroscopy.]}

Using the \mbh\ estimator introduced in Section~\ref{mbh}, we estimate the value of \mbh\ and select the targets meets range $7.5 \lesssim {\rm log}$~\mbh$\lesssim8.5$.
The bolometric luminosities presented in \citet{Schulze2018} enable us to calculate their Eddington ratio $\lambda = L_{\rm bol}/L_{\rm Edd}$ and select the sample which meets our selection window, as shown in Figure~\ref{fig:selection}. Moreover, we have higher preference to select the target which has rest-frame UV images as provided by \citet{Scoville2007}.

We list all the AGN systems analyzed in this work in Table~\ref{tab:objlist}.

%\subsection{Black hole mass and Eddington ratios}
\begin{figure}
\centering
{
\includegraphics[height=0.5\textwidth]{fig/AGN_selection.pdf}
}
\caption{\label{fig:selection} 
We present the selection window as used to choose our AGN sample, which is based on the Eddington ratios ($\lambda = L_{\rm Bol}/L_{\rm Edd}$) and \mbh. Our sample (color coded) falls well below the knee of BH mass function at $z=1.5$ \citep[top panel,][]{Schulze2015}. For comparing propose, we plot the high-$z$ luminous SDSS QSO samples that has been studied based on the observation of \hst\ in the reference~\citep[grey squares and circles from][respectively]{Peng2006a, Decarli2010}. 
}
\end{figure}

\begin{deluxetable*}{llccccc}
\tablecolumns{7}
\tablewidth{0pt}
\tablecaption{Details of Observation} 
\tablehead{ 
\colhead{Object ID} &
\colhead{$z$} & 
\colhead{WFC3/Filter} &
\colhead{$RA$}&
\colhead{$DEC$}&
\colhead{Observing date}&
\colhead{Exposure time (s)}
\\ 
\colhead{(1)} &
\colhead{(2)} &
\colhead{(3)} &
\colhead{(4)} &
\colhead{(5)} &
\colhead{(6)} &
\colhead{(7)}
} 
\startdata
%\multicolumn{5}{c}{Sample presented in \citet{Treu+07}}\\
%\\
COSMOS-CID1174 & 1.552 & F140W & 150.2789 & 1.9595 & 2017-10-26 & 2395.4\\
COSMOS-CID1281 & 1.445 & F140W & 150.4160 & 2.5258 & 2018-11-26 & 2395.4\\
COSMOS-CID206 & 1.483 & F140W & 149.8371 & 2.0088 & 2017-10-23 & 2395.4\\
COSMOS-CID216 & 1.567 & F140W & 149.7918 & 1.8729 & 2017-10-23 & 2395.4\\
COSMOS-CID237 & 1.618 & F140W & 149.9916 & 1.7243 & 2018-06-03 & 2395.4\\
COSMOS-CID255\footnoteref{note1} & 1.664 & F140W & 150.1017 & 1.8483 & 2019-03-16 & 2395.4\\
COSMOS-CID3242 & 1.532 & F140W & 149.7113 & 2.1452 & 2017-10-26 & 2395.4\\
COSMOS-CID3570 & 1.244 & F125W & 149.6411 & 2.1076 & 2017-10-27 & 2395.4\\
COSMOS-CID452 & 1.407 & F125W & 150.0045 & 2.2371 & 2017-10-25 & 2395.4\\
COSMOS-CID454 & 1.478 & F140W & 149.8681 & 2.3307 & 2018-02-26 & 2395.4\\
COSMOS-CID50 & 1.239 & F125W & 150.2080 & 2.0833 & 2017-10-23 & 2395.4\\
COSMOS-CID543 & 1.301 & F125W & 150.4519 & 2.1448 & 2018-04-30 & 2395.4\\
COSMOS-CID597 & 1.272 & F125W & 150.5262 & 2.2449 & 2018-11-25 & 2395.4\\
COSMOS-CID607 & 1.294 & F125W & 150.6097 & 2.3231 & 2017-10-25 & 2395.4\\
COSMOS-CID70 & 1.667 & F140W & 150.4051 & 2.2701 & 2017-10-27 & 2395.4\\
COSMOS-LID1273 & 1.617 & F140W & 150.0565 & 1.6275 & 2017-10-31 & 2395.4\\
COSMOS-LID1538 & 1.527 & F140W & 150.6215 & 2.1588 & 2018-05-01 & 2395.4\\
COSMOS-LID360 & 1.579 & F140W & 150.1251 & 2.8617 & 2017-10-30 & 2395.4\\
COSMOS-XID2138 & 1.551 & F140W & 149.7036 & 2.5781 & 2017-11-01 & 2395.4\\
COSMOS-XID2202 & 1.516 & F140W & 150.6530 & 1.9969 & 2017-11-05 & 2395.4\\
COSMOS-XID2396 & 1.600 & F140W & 149.4779 & 2.6425 & 2017-11-12& 2395.4\\
CDFS-1 & 1.630 & F140W & 52.8990 & -27.8600 & 2018-04-03 & 2395.4\\
CDFS-229 & 1.326 & F125W & 53.0680 & -27.6580 & 2018-04-04 & 2395.4\\ 
CDFS-321 & 1.570 & F140W & 53.0486 & -27.6239 & 2018-08-18& 2395.4\\ 
CDFS-724 & 1.337 & F125W & 53.2870 & -27.6940 & 2018-04-05 & 2395.4\\ 
ECDFS-358 & 1.626 & F140W & 53.0850 & -28.0370 & 2018-02-09& 2395.4\\ 
SXDS-X1136 & 1.325 & F125W & 34.8925 & -5.1498 & 2018-01-29& 2395.4\\ 
SXDS-X50 & 1.411 & F125W & 34.0267 & -5.0602 & 2018-03-01& 2395.4\\ 
SXDS-X717 & 1.276 & F125W & 34.5400 & -5.0334 & 2018-07-02 & 2395.4\\ 
SXDS-X735 & 1.447 & F140W & 34.5581 & -4.8781 & 2017-11-14 & 2395.4\\ 
SXDS-X763 & 1.412 & F125W & 34.5849 & -4.7864 & 2018-07-03 & 2395.4\\ 
SXDS-X969 & 1.585 & F140W & 34.7594 & -5.4291 & 2018-07-02 & 2395.4\\ 
\enddata
\label{tab:objlist}
\tablecomments{
Column 1: Object field and ID.
Column 2: Redshifts.
Column 3: WFC3 filter. Note that the targets from the COSMOS field also have ACS/F814W imaging.
Column 4 and 5: J2000 $RA$ and $DEC$ coordinates.
Column 6: The observing start date.
}
\end{deluxetable*}

\subsection{BH masses}
\label{mbh}
The \mbh\ of type-1 AGNs can be inferred using the so-called virial method~\citep{Peterson2004, Shen2013}. The kinematics of the broad-line region (BLR) trace the gravitational field of the central supermassive black hole, assuming the gravity dominates the motion of the BLR gas. In this scenario, the width of the emission-line provided the scale of the velocity, while the AGN continuum luminosity establish an empirical scale of the BLR size. As a result, the estimation of the \mbh\ is achieved by these measurements.

To avoid any systematic bias between our samples and the literature ones, we compared the recipes as introduced by \citet{Schulze2018, Ding2017b}. We find that the \hbeta\ estimator is very consistent (\mbh\ r.m.s. $<0.03$~dex) between the two references. We also find that, in \citet{Schulze2018}, the cross-calibration between the \halpha\ and \hbeta\ has better agreement. Thus, we adopt the virial formalism from \citet{Schulze2018}:
